Detailed structure of phospholipid bilayers with negatively charged lipids and salt concentrations from molecular dynamics simulations including the effects of electronic polarization

### 2019-05-14 Manuscript/manuscript.tex
Included the dihedral distribution figure in the text.

Despite the success in simulating bilayer dimensions and acyl chain conformations,
lipid force fields have typically problems in capturing the correct glycerol backbone and
headgroup order parameters and conformations \cite{botan15,ollila16,NMRlipidsIV}.
This is the case also for Lipid17 POPS simulations, where the headgroup and glycerol backbone
order parameters are quite far from experimental values with both Dang (Fig. \ref{simVSexpNOions_POPS})
and {\AA}qvist \cite{NMRlipidsIV} ions. The values from ECC-POPS simulation are closer,
but not in full agreement with experiments (Fig.~\ref{simVSexpNOions_POPS}).
Especially, the experimentally observed more negative values of the $\beta$-carbon
and the larger forking (difference of order parameters between hydrogens attached to the
same carbon \cite{ollila16}) of the $\alpha$-carbon in POPS than in POPC \cite{NMRlipidsIV}
are not reproduced by neither of the models here. 
These differences are previously related
to a more rigid structure of PS headgroup and 
the stiffness of the C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$ dihedral. 
Interestingely, this dihedral angle is more flexible in ECC-POPS compared to Lipid17 
suggesting that its rigidity is overestimated in Lipid17 due to the lack of electronic polarizability,
while the same dihedral parameters yield too small forking in ECC-POPS.
\todo{the dihedral to be plotted.}
Although the ECC-POPS model reproduces the lipid bilayer dimensions and
acyl chain conformations in a good agreement with experiments, 
there is a room for improvements especially in the glycerol backbone and headgroup region,
e.g. in the parameters of the associated dihedral angles. 
\cite{botan15, ollila16, Pluhackova2016, NMRlipidsIV}.

>>>>

Despite the success in simulating bilayer dimensions and acyl chain conformations,
lipid force fields have typically problems in capturing the correct glycerol backbone and
headgroup order parameters and conformations \cite{botan15,ollila16,NMRlipidsIV}.
This is the case also for Lipid17 POPS simulations, where the headgroup and glycerol backbone
order parameters are quite far from experimental values with both Dang (Fig. \ref{simVSexpNOions_POPS})
and {\AA}qvist \cite{NMRlipidsIV} ions. The values from ECC-POPS simulation are closer,
but not in full agreement with experiments (Fig.~\ref{simVSexpNOions_POPS}).
Especially, the experimentally observed more negative values of the $\beta$-carbon
and the larger forking (difference of order parameters between hydrogens attached to the
same carbon \cite{ollila16}) of the $\alpha$-carbon in POPS than in POPC \cite{NMRlipidsIV}
are not reproduced by neither of the models here. 
These differences are previously related
to a more rigid structure of PS headgroup and 
the stiffness of the C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$ dihedral
plotted in Fig.~\ref{fig:dihedral}. 
Interestingely, this dihedral angle is more flexible in ECC-POPS compared to Lipid17 
suggesting that its rigidity is overestimated in Lipid17 due to the lack of electronic polarizability,
while the same dihedral parameters yield too small forking in ECC-POPS.
Although the ECC-POPS model reproduces the lipid bilayer dimensions and
acyl chain conformations in a good agreement with experiments, 
there is a room for improvements especially in the glycerol backbone and headgroup region,
e.g. in the parameters of the associated dihedral angles. 
\cite{botan15, ollila16, Pluhackova2016, NMRlipidsIV}.

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/dihedral_angle_distribution_Ca-Cb-Cg-Og_ECC-L17.pdf}
  \caption{\label{fig:dihedral}
    Distribution of dihedral angle \ce{C_\alpha-C_\beta-C_\gamma-O_\gamma} in POPS 
    from simulations of a pure POPS bilayer with \ce{Na+} counterions using Lipid17 and ECC-lipids. 
}
\end{figure}
